Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-10-04 manuscript.Rmd
Boxplot updates.

>>>>

```{r Figure 1 Boxplot of Article Counts}
library(gridExtra)

set.seed(1237)
boxplot_swhd <- n.so.yr %>% 
  select(Journal, n)%>%
  mutate(index = rep("SWHD")) %>%
  group_by(Journal)

boxplot_swhd <- data.frame(boxplot_swhd)
top_3_swhd <- boxplot_swhd %>% slice(1:3)

boxplot_scopus <- scopus.df %>%
  select(Journal, Documents) %>%
  filter(Documents > 0) %>%
  rename(n = Documents) %>%
  mutate(index = rep("Scopus"))
boxplot_scopus <- data.frame(boxplot_scopus)  
boxplot_scopus <- boxplot_scopus %>% group_by(Journal) %>%
  summarize(n = sum(n)) %>%
  mutate(index = rep("Scopus"))

boxplot_df <- rbind(boxplot_swhd, boxplot_scopus)

swhd_bp <- ggplot(data=boxplot_swhd, aes(x = index, y=n)) +
  stat_boxplot(geom="errorbar") +
  geom_boxplot(outlier.size = 0) +
  theme_bw() + 
  geom_jitter(colour = cp[2], alpha = .60, size = 4) + 
  ylab("Number of Articles") + 
  #xlab("Database") + 
  ylim(c(0, 1600)) + 
  xlab("") + 
  annotate("text", x = c(1.18, 1.15, .9), y = c(top_3_swhd$n[1], top_3_swhd$n[2], top_3_swhd$n[3]), label = top_3_swhd$Journal)

scopus_bp <- ggplot(data=boxplot_scopus, aes(x = index, y=n)) +
  stat_boxplot(geom="errorbar") +
  geom_boxplot(outlier.size = 0) +
  theme_bw() + 
  geom_jitter(colour = cp[4], alpha = .60, size = 4) + 
  ylab("") + 
  #xlab("Database") + 
  ylim(c(0, 1600)) + 
  theme(axis.text.y = element_blank()) +
  xlab("")

grid.arrange(swhd_bp, scopus_bp, ncol=2)

  ylab("Cumulative article count") +
  annotate("text", x = 0.87, y = 1600, label = "Families in Society")+
  annotate("text", x = 0.91, y = 1400, label = "Social Work") +
  annotate("text", x = 1.20, y = 1350, label = "British Journal of Social Work")+
  theme_bw()+
  theme(axis.title.x = element_blank()) +
  theme(panel.border = element_blank(), axis.line = element_line())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_x_discrete(breaks=NULL)+
  theme(plot.title = element_text(size = 18))+
  theme(axis.text=element_text(size=10), axis.title=element_text(size=16))
